noam_data_exploration_v1

### 2024-08-20 noam_data_exploration_v3.Rmd
started adding in effects size plots from emmeans

```{r glmm approach}
alpha_diversity_quad$year_factor <- as.factor(alpha_diversity_quad$year) # for glmmTMB ar1 structure
# Framing - is adiv generally higher in certain habitats/regions?

@@

summary(richness_mod_2) # looks like strong autocorrelation, which makes sense to me
Anova(richness_mod_2)
plot(allEffects(richness_mod_2))
# emmeans(richness_mod_2, pairwise ~ habitat | year_factor) # if we want to compare habitats year to year
# model.sel(dredge(richness_mod_2))

>>>>

```{r glmm approach, fig.height = 15, fig.width=20}
alpha_diversity_quad$year_factor <- as.factor(alpha_diversity_quad$year) # for glmmTMB ar1 structure
# Framing - is adiv generally higher in certain habitats/regions?

@@

summary(richness_mod_2) # looks like strong autocorrelation, which makes sense to me
Anova(richness_mod_2)
plot(allEffects(richness_mod_2))
mod_emm <- emmeans(richness_mod_2, ~ habitat * island_side * year_factor) # if we want to compare habitats year to year
plot(mod_emm) +
  geom_point(aes(x = emmean, y = year_factor, colour = habitat))
  facet_wrap(island_side~habitat)
# model.sel(dredge(richness_mod_2))

emmip(richness_mod_2, island_side ~ year_factor | habitat, CIs = TRUE) +
  scale_colour_manual(values = island_side_colours) +
  scale_shape_manual(values = habitat_shapes) +
  scale_y_continuous(limits = c(0,2)) +
#  facet_wrap(~habitat)+
#  labs(title = "b. shannon quad level\n", y = "shannon\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        )
